Output Summary

### 2023-04-12 03-post-process/output-plots-children/05-length.Rmd
Update file names on output-plots children

# Length-Based Quantities {.tabset .tabset-dropdown}

## Mean Parr Length vs. Egg Density

```{r}
plot_f = function(j) {

@@

xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, xlab)
mtext(side = 2, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
```

@@

### "Growth Factor" vs. Parr Mean Length

```{r}
plot_f = function(j) {

@@

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, TeX("$Mean\\,Length\\,at\\,Summer\\,Tagging\\,(mm)$"))
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr\\,\\rightarrow\\, Spring\\,Smolt\\,Growth\\, Factor$"))
```

### "Growth Factor" Time Series

```{r}
plot_f = function(j) {
  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               Delta_L_Pb_Mb_obs,
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow Spring\\,Smolt\\,Growth\\, Factor$"))
```

## Parr $\rightarrow$ Smolt Overwinter Survival vs. Parr Mean Length

```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
plot_fn = function(j, i) {

  # extract posterior summaries of spring length outcomes
  L_Pb_mean = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["mean",]
  L_Pb_lwr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
  L_Pb_upr = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))["97.5%",]

@@

  # summarize posterior of overwinter survival outcomes
  phi_Pa_Mb_mean = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["mean",])[-1,i,j]
  phi_Pa_Mb_lwr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["2.5%",])[-1,i,j]
  phi_Pa_Mb_upr = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", pop = j, year = ts_yrs, LH_type = i))["97.5%",])[-1,i,j]

  # create vectors to predict survival at: for credible regions and mean curve
  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
  L_Pb_star_seq = seq(min(L_Pb_star_lwr), max(L_Pb_star_upr), length = 30)

  # extract posteriors of coefficients
  gamma0 = post_subset(post, sub_index("gamma0[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)
  gamma1 = post_subset(post, sub_index("gamma1[LH_type,pop]", pop = j, LH_type = i), matrix = TRUE)

  # function to create predicted survival curve for one posterior sample
  pred_fn = function(i) {
    pred_phi_Pa_Mb = plogis(gamma0[i] + gamma1[i] * L_Pb_star_seq)
    names(pred_phi_Pa_Mb) = paste0("pred_phi_Pa_Mb[", 1:30, "]")
    pred_phi_Pa_Mb
  }

  # calculate predicted survivals and add to posterior samples
  pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
  post_pred_phi_Pa_Mb = post_convert(cbind(postpack:::id_mat(post), pred_phi_Pa_Mb))

  # extract summarize predicted length
  pred_phi_Pa_Mb_mean = post_summ(post_pred_phi_Pa_Mb, ".")["mean",]
  pred_phi_Pa_Mb_lwr = post_summ(post_pred_phi_Pa_Mb, ".")["2.5%",]
  pred_phi_Pa_Mb_upr = post_summ(post_pred_phi_Pa_Mb, ".")["97.5%",]

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
       xlim = range(L_Pb_seq), 
       main = ifelse(i == 1, pops[j], "")
  )

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_phi_Pa_Mb_lwr, rev(pred_phi_Pa_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_phi_Pa_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_phi_Pa_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(phi_Pa_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

plot_fn2 = function(j) {
    # create the plots for both migratory strategies
  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
}

par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn2)
mtext(side = 1, line = 1.5, outer = T, "Mean Length at Summer Tagging (mm)", cex = 1.2)
mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
```

## Smolt Survival to LGR vs. Smolt Mean Length

```{r toLGR-survival-plots, fig.width = 6, fig.height = 5}
plot_fn = function(j, i) {

  # extract posterior summaries of spring length outcomes
  L_Mb_mean = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
  L_Mb_lwr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
  L_Mb_upr = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]

  # obtain scaled/centered versions
  L_Mb_star_mean = (L_Mb_mean - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
  L_Mb_star_lwr = (L_Mb_lwr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
  L_Mb_star_upr = (L_Mb_upr - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]

  # summarize posterior of migration survival outcomes
  phi_Mb_Ma_mean = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["mean",])[-1,i_spring,o_nor,j]
  phi_Mb_Ma_lwr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["2.5%",])[-1,i_spring,o_nor,j]
  phi_Mb_Ma_upr = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = j, year = ts_yrs, LH_type = i_spring, origin = o_nor))["97.5%",])[-1,i_spring,o_nor,j]

  # create vectors to predict survival at: for credible regions and mean curve
  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)

  # extract posteriors of coefficients
  tau0 = post_subset(post, sub_index("tau0[pop]", pop = j), matrix = TRUE)
  tau1 = post_subset(post, sub_index("tau1[pop]", pop = j), matrix = TRUE)

  # function to create predicted survival curve for one posterior sample
  pred_fn = function(i) {
    pred_phi_Mb_Ma = plogis(tau0[i] + tau1[i] * L_Mb_star_seq)
    names(pred_phi_Mb_Ma) = paste0("pred_phi_Mb_Ma[", 1:30, "]")
    pred_phi_Mb_Ma
  }

  # calculate predicted survivals and add to posterior samples
  pred_phi_Mb_Ma = t(sapply(1:post_dim(post, "saved"), pred_fn))
  post_pred_phi_Mb_Ma = post_convert(cbind(postpack:::id_mat(post), pred_phi_Mb_Ma))

  # extract summarize predicted length
  pred_phi_Mb_Ma_mean = post_summ(post_pred_phi_Mb_Ma, ".")["mean",]
  pred_phi_Mb_Ma_lwr = post_summ(post_pred_phi_Mb_Ma, ".")["2.5%",]
  pred_phi_Mb_Ma_upr = post_summ(post_pred_phi_Mb_Ma, ".")["97.5%",]

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
       xlim = range(L_Mb_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_phi_Mb_Ma_lwr ~ L_Mb_seq, col = "red", lty = 2)
  lines(pred_phi_Mb_Ma_upr ~ L_Mb_seq, col = "red", lty = 2)
  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Mb_lwr, phi_Mb_Ma_mean, L_Mb_upr, phi_Mb_Ma_mean, col = alpha("red", 0.5))
  segments(L_Mb_mean, phi_Mb_Ma_lwr, L_Mb_mean, phi_Mb_Ma_upr, col = alpha("red", 0.5))
  points(phi_Mb_Ma_mean ~ L_Mb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(phi_Mb_Ma_mean ~ L_Mb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Length at Spring Tagging (mm)")
mtext(side = 2, outer = T, line = 0.25, "Migration to LGR Survival")
```

>>>>

# Parr & Smolt Mean Length {.tabset .tabset-pills}

## Parr Mean Length {.tabset .tabset-pills}

### Time Series {.tabset .tabset-pills}

#### Realized Alone

```{r L_Pb_tseries-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Parr Mean Length (mm)")
```

#### Realized & Predicted

```{r L_Pb_tseries-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )

  # draw the predicted time series
  add_tseries(est = post_summ(post, sub_index("^L_Pb_dot[year,pop]", pop = j, year = ts_yrs)),
              yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Parr Mean Length (mm)")
```

### Density-Dependent Relationship

```{r L_Pb-relationship, fig.width = 6, fig.height = 5}
plot_f = function(j) {

@@

xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, xlab)
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\,(mm)$"))
```

@@

### Time Series {.tabset .tabset-pills}

#### Realized Alone

```{r L_Mb-tseries-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
```

#### Realized & Predicted

```{r get-L_Mb_dot}
# function to get posterior samples of expected smolt length
# not calculated in JAGS model, add to post object here
f = function() {
  # extract posterior samples of parr mean length and parr to smolt growth factor
  L_Pb = post_subset(post, "^L_Pb[", matrix = TRUE)
  Delta_L_Pb_Mb_dot = post_subset(post, "^Delta_L_Pb_Mb_dot[", matrix = TRUE)

  # perform basic operations for one iteration -- for making dimension names later
  L_Pb_1 = array_format(L_Pb[1,])
  Delta_L_Pb_Mb_dot_1 = array_format(Delta_L_Pb_Mb_dot[1,])
  L_Mb_dot_1 = L_Pb_1 * Delta_L_Pb_Mb_dot_1

  # function to perform the calculation for one MCMC sample
  g = function(i) {
    L_Pb_i = array_format(L_Pb[i,])
    Delta_L_Pb_Mb_dot_i = array_format(Delta_L_Pb_Mb_dot[i,])
    L_Mb_dot_i = L_Pb_i * Delta_L_Pb_Mb_dot_i
    as.numeric(L_Mb_dot_i)
  }

  # apply to each posterior sample
  out = t(sapply(1:nrow(L_Pb), g))

  # build element indices: the year
  y_ind = rep(1:nrow(L_Pb_1), ncol(L_Pb_1))

  # build element indices: the population
  j_ind = rep(1:ncol(L_Pb_1), each = nrow(L_Pb_1))

  # make element names
  colnames(out) = paste0("L_Mb_dot[", y_ind, ",", j_ind, "]")

  # drop out those that have NA values (first k_max years)
  na_ind = which(!is.na(out[1,]))
  out[,na_ind]
}

# combine with the rest of the posterior samples
post = post_bind(post, f()); rm(f)
```

```{r L_Mb-tseries-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )

  # draw the realized time series
  add_tseries(est = post_summ(post, sub_index("^L_Mb_dot[year,pop]", year = ts_yrs, pop = j)),
              yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
```

## Parr $\to$ Smolt "Growth" Factor {.tabset .tabset-pills}

### Time Series {.tabset .tabset-pills}

#### Realized Alone

```{r Delta_L_Pb_Mb-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
```

#### Realized & "Data"

```{r Delta_L_Pb_Mb-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               Delta_L_Pb_Mb_obs, main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
```

#### Realized & Predicted

```{r Delta_L_Pb_Mb-3, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # draw the realized time series
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = c(1,2))

  # draw the predicted time series
  add_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb_dot[year,pop]", pop = j, year = ts_yrs)),
              yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
```

### Relationship

```{r Delta_L_Pb_Mb-relationship, fig.width = 6, fig.height = 5}
plot_f = function(j) {

@@

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\, (mm)$"))
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, \\to\\, Smolt\\, Growth\\, Factor$"))
```

## Smolt vs. Parr Mean Length

```{r L_Mb-v-L_Pb, fig.width = 6, fig.height = 5}
plot_fn = function(j) {

  # extract posterior summaries of parr mean length outcomes
  L_Pb_summ = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j))
  L_Pb_mean = L_Pb_summ["mean",]
  L_Pb_lwr = L_Pb_summ["2.5%",]
  L_Pb_upr = L_Pb_summ["97.5%",]

  # extract posterior summaries of parr mean length outcomes
  L_Mb_summ = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j))
  L_Mb_mean = L_Mb_summ["mean",]
  L_Mb_lwr = L_Mb_summ["2.5%",]
  L_Mb_upr = L_Mb_summ["97.5%",]

@@

  # create vectors to predict smolt mean length at: for credible regions and mean curve
  L_Pb_seq = seq(min(L_Pb_lwr), max(L_Pb_upr), length = 30)
  L_Pb_star_seq = seq(min(L_Pb_star_lwr), max(L_Pb_star_upr), length = 30)

  # function to create predicted survival curve for one posterior sample
  pred_fn = function(i) {
    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
    pred_L_Mb = L_Pb_seq * pred_Delta_L_Pb_Mb
    names(pred_L_Mb) = paste0("pred_L_Mb[", 1:30, "]")
    pred_L_Mb
  }

  # calculate predicted survivals and add to posterior samples
  pred_L_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
  post_pred_L_Mb = post_convert(cbind(postpack:::id_mat(post), pred_L_Mb))

  # extract summarize predicted length
  pred_L_Mb_summ = post_summ(post_pred_L_Mb, ".")
  pred_L_Mb_mean = pred_L_Mb_summ["mean",]
  pred_L_Mb_lwr = pred_L_Mb_summ["2.5%",]
  pred_L_Mb_upr = pred_L_Mb_summ["97.5%",]

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_L_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_L_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_L_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, L_Mb_mean, L_Pb_upr, L_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, L_Mb_lwr, L_Pb_mean, L_Mb_upr, col = alpha("red", 0.5))
  points(L_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(L_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Parr Mean Length (mm)")
mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
```

### 2023-04-12 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Update file names on output-plots children

# "growth" factor
qresid_post = cbind(qresid_post,
                    make_qresid_all("^Delta_L_Pb_Mb[year,pop]",
                                    "^Delta_L_Pb_Mb_dot[year,pop]",
                                    "sig_Lphi_Pa_Mb[pop]",
                                    type = "pop", f_real = log, f_mean = log)
)

>>>>

# "growth" factor
qresid_post = cbind(qresid_post,
                    make_qresid_all("^Delta_L_Pb_Mb[year,pop]",
                                    "^Delta_L_Pb_Mb_dot[year,pop]",
                                    "sig_lDelta_L_Pb_Mb[pop]",
                                    type = "pop", f_real = log, f_mean = log)
)

### 2023-04-12 03-post-process/output-plots.Rmd
Update file names on output-plots children

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "siw"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

@@

```{r mean-length, child = "output-plots-children/05-length-based-values.Rmd", eval = params$include_mean_length}
```

@@

```{r capacity-vs-habitat, child = "output-plots-children/06-capacity-vs-habitat.Rmd", eval = params$include_capacity_vs_habitat}
```

```{r misc-process-model, child = "output-plots-children/07-misc-process-model.Rmd", eval = params$include_misc_process_model}
```

```{r equiv-rates, child = "output-plots-children/08-equiv-rates.Rmd", eval = params$include_equiv_rates}
```

```{r rho-params, child = "output-plots-children/09-rho-params.Rmd", eval = params$include_rho_params}
```

```{r noise-term-diags, child = "output-plots-children/10-noise-term-diags.Rmd", eval = params$include_noise_term_diags}
```

```{r param-summaries, child = "output-plots-children/11-param-summaries.Rmd", eval = params$include_param_summaries}
```

```{r jags-info, child = "output-plots-children/12-jags-model-info.Rmd", eval = params$include_jags_info}
```

@@

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "siw"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

@@

```{r mean-length, child = "output-plots-children/05-length.Rmd", eval = params$include_mean_length}
```

@@

```{r capacity-vs-habitat, child = "output-plots-children/07-capacity-vs-habitat.Rmd", eval = params$include_capacity_vs_habitat}
```

```{r misc-process-model, child = "output-plots-children/08-misc-process-model.Rmd", eval = params$include_misc_process_model}
```

```{r equiv-rates, child = "output-plots-children/09-equiv-rates.Rmd", eval = params$include_equiv_rates}
```

```{r rho-params, child = "output-plots-children/10-rho-params.Rmd", eval = params$include_rho_params}
```

```{r noise-term-diags, child = "output-plots-children/11-noise-term-diags.Rmd", eval = params$include_noise_term_diags}
```

```{r param-summaries, child = "output-plots-children/12-param-summaries.Rmd", eval = params$include_param_summaries}
```

@@

```{r jags-info, child = "output-plots-children/14-jags-model-info.Rmd", eval = params$include_jags_info}
```
